{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2025-01-10 Notebook LaTEX/Proposal/main.tex
>w<, sync

\section{Introduction}
    Let $\RR^n$ be the ambient space. We consider 
    \begin{align}
        \min_{x \in \RR^n} \left\lbrace
            F(x): f(x) + g(x)
        \right\rbrace.
    \end{align}\label{eqn:additive-comp-obj}
    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:Q \rightarrow \overline \RR$ is convex. 
    This type of problem is referred to as additive composite problems in the literature. 
    \par
    Our ongoing research concerns accelerated proximal gradient type method for solving (\ref{eqn:additive-comp-obj}). 
    In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
    We had some lingering questions after reading it. 
    \begin{enumerate}
        \item Do there exist a unified description for the convergence for both variants of the algorithms?
        \item Is it possible to attain fast convergence rate without knowledge about the strong convexity of function $f$?
        \item Is it possible to describe the convergence of function value for momentum sequences that are much weaker than the Nesterov's rule? 
    \end{enumerate}
    The good news is we have definitive answers for all questions by our own efforts of research. 
    \todoinline{\noindent
        $\square$ Change all the organization parts here
    }
    Section \ref{sec:unify-nes-acceleration}, \ref{sec:free-rwapg} are our ongoing research which present the answers to the questions. 
    \par
    In Section \ref{sec:unify-nes-acceleration}, we proposed the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures. 
    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures. 
    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
    \par
    In Section \ref{sec:free-rwapg} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior. 
    Results of numerical experiments are presented. 
    \par
    Section \ref{sec:catalyst} complements report completed for MATH 590 Fall Winter 2024. 
    It's based on a series of recent papers \cite{lin_universal_2015,lin_catalyst_2018,paquette_catalyst_2018} about Catalyst Meta Acceleration for First Order Variance Reduced Methods. 
    The end of Section \ref{sec:catalyst} points out potential future direction of research of Catalyst Acceleration. 
    % \par
    % Section \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in nonsmooth optimization frontier research where progress and impacts can be made.  
    \subsection{Theme of the research}
        This section specifies a theme of the research in this proposal. 
        Firstly, we explore the Goldilocks zones between these topics: Nesterov's acceleration, algorithms with inexact evaluation of the proximal point operator, and applications.  
        In doing so, we identify the ``chemistry'' between various properties of functions and the affect it has on the designs/behaviors of first order algorithm for continuous optimization.

>>>>

\section{Introduction}
    Let $\RR^n$ be the ambient space. We consider 
    \begin{align}
        \min_{x \in \RR^n} \left\lbrace
            F(x): f(x) + g(x)
        \right\rbrace.
    \end{align}\label{eqn:additive-comp-obj}
    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:Q \rightarrow \overline \RR$ is convex. 
    This type of problem is referred to as additive composite problems in the literature. 
    \par
    Our ongoing research concerns accelerated proximal gradient type method for solving (\ref{eqn:additive-comp-obj}). 
    In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
    We had some lingering questions after reading it. 
    \begin{enumerate}
        \item Do there exist a unified description for the convergence for both variants of the algorithms?
        \item Is it possible to attain fast convergence rate without knowledge about the strong convexity of function $f$?
        \item Is it possible to describe the convergence of function value for momentum sequences that are much weaker than the Nesterov's rule? 
    \end{enumerate}
    The good news is we have definitive answers for all questions by our own efforts of research. 
    Section \ref{sec:unify-nes-acceleration}, proposes the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures. 
    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures. 
    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
    \par
    Section \ref{sec:free-rwapg} proposes a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without restarting and knowing parameter $L, \mu$ in prior. 
    Results of numerical experiments are presented. 
    \par
    Section \ref{sec:catalyst} complements report completed for MATH 590 Fall Winter 2024. 
    It's based on a series of recent papers \cite{lin_universal_2015,lin_catalyst_2018,paquette_catalyst_2018} about Catalyst Meta Acceleration for First Order Variance Reduced Methods. 
    The end of Section \ref{sec:catalyst} points out potential future direction of research of Catalyst Acceleration. 
    % \par
    % Section \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in nonsmooth optimization frontier research where progress and impacts can be made.  
    \subsection{Theme of the research}
        This section specifies a theme of the research in this proposal. 
        Firstly, we explore the Goldilocks zones between these topics: Nesterov's acceleration, algorithms with inexact evaluation of the proximal point operator, and applications.  
        In doing so, we identify the ``chemistry'' between various properties of functions and the affect it has on the designs/behaviors of first order algorithm for continuous optimization.
